### 2021-07-05 chapters/7_discussion.tex
rq1 discussion finished

\chapter{Discussion}
\label{ch:discussion}
In this chapter, we discuss the results of our experiments on clustering the mutants.

\begin{finding}
	Highlight like this an important finding of your analysis of the results.
	\label{find:important1}
\end{finding}

Refer to Finding~\ref{find:important1}.

\section{Threats to validity}
What could affect the validity of your research? Think of pitfalls of your research method, experimental setup, interpreting the results.
- pit generated mutants -> it's hard to know if we can cluster ALL posible mutants
- Selected sources
- equivalent mutants

>>>>

\chapter{Discussion}
\label{ch:discussion}
In this chapter, we discuss the results of our experiments on clustering the mutants.
We will first discuss the results of the first experiment. 
For the first experiment will discuss the all the results together and compare the results between the variants.
Secondly we will discuss the results of the second experiment.
Thirdly we will discuss how the results both experiments compare to each other.
And last we will discuss the practicality of our research.s

\section{RQ 1: Identifying and clustering mutant characteristics}
The maximum deviation from the original mutation score, for all variants(with and without Levenshtein distance) of the experiment, are below the statistical 
As hypothesised we observe that it is possible to cluster mutants with the set of characteristics we identified while maintaining effectiveness and reducing the amount executed.
The hypothesis holds for all the projects and variants of the experiment.
Most of the projects had a deviation of less than 1\% for all variations.

\begin{finding}
    With a reduction up to 75\% of the total amount of mutants we can still maintain effectiveness.
\end{finding}
In both variants we observe a reduction in average accuracy when reducing the amount of clusters.
This reductions is 0.1\% for clustering with all characteristics and 0.04\% for clustering without Levenshtein distance.
We can also see that the average cluster accuracy is lower when reducing the amount executed.
\begin{finding}
    The more you reduce the amount of mutants executed the more accuracy is lost.
\end{finding}
The results show that the average accuracy for reductions of 25\% and 50\% is the same.
This observation shows true for both variants of the experiment which is remarkable.
\begin{finding}
    In our data set it is safe to reduce the mutants by half without reducing the accuracy.
\end{finding}
It is also remarkable to see the min and max accuracy of the all clusters are 50\% to 100\% respectively.
Based on these results we can state the following:
\begin{itemize}
    \item For every project there was at least one cluster that consisted only of killed or survived mutants.
    \item For every project there was at least one cluster that evenly divided between killed and survived mutants.
\end{itemize}
With the exception of all Google Auto Service and Commons Text with a reduction of 25\% and all characteristics all projects showed an average accuracy above 90\%.
The combination of hierarchical clustering and the identified characteristics results in high accuracy clusters.
As logic dictates we expect that a higher accuracy means a score closer to that of the original.
However we do not observe this behaviour in our results.
This is due to our random sampling method.
If we would select a mutant in the majority of each cluster the accuracy per cluster would correlate to the deviation in mutation score.
Unfortunately we do not know the majority of a cluster as we do now know if a mutant survives or is killed before execution.
\begin{finding}
    Random sampling a mutant per cluster may result in a lower mutation score.
\end{finding}
As stated in Chapter \ref{ch:results_rq1} the calculation of the Levenshtein distance took a long time.
For this reason we repeated the experiment without the Levenshtein distance.
Comparing the results between these variants we can observe a max deviation of 0.05\% between average difference of the mutation score of.
In 66\% of the results displayed in Chapter \ref{ch:results_rq1} clustering without the Levenshtein distance is more accurate.
The biggest difference measured between all the projects and their reductions is 2.13\% where of clustering without Levenshtein distance was more accurate.
\begin{finding}
    While clustering without the Levenshtein distance was more accurate in our results, the Levenshtein distance characteristic does not significantly increase or decrease the cluster accuracy.
\end{finding}

The application of our research is limited to all software projects written in the language Java and the limitations of our mutation testing tool PIT\cite{pit}.
This scope is significantly larger than most of the research done in the domain of mutation clustering(Chapter \ref{ch:related_work}).

\section{Threats to validity}
What could affect the validity of your research? Think of pitfalls of your research method, experimental setup, interpreting the results.
- pit generated mutants -> it's hard to know if we can cluster ALL possible mutants
- Selected sources
- equivalent mutants

### 2021-07-05 chapters/rq2/1_experiment_design.tex
Added abstract
rq1 discussion finished

\subsection{Training strategy}
\label{ch:training_strategy}
Our data set contains of mutants represented by their characteristics. 
The characteristics of the mutants are generated per project and have a project specific context.
The relations between the different mutants are also specific per project.
For example mutant with a mutator in a certain project can have a different effect on the source code and can give other results than a mutator in a different project.
To keep the relations and context we decided to train a model per project.
\newline
To validate the model we need to split our data set into a training set and a validation set.
Our total data set consists of approximately 1 million mutants generated over fourteen projects.
Research has shown that if the data set is big enough a ratio of 80/20 is sufficient\cite{Guyon1997ARatio}.
We will divide each source projects into training and validation groups to reflect the 80/20 ratio as best as possible.
Depending on the amount of mutants per project we might not achieve a perfect 80/20 ratio.

@@

\subsection{Validation}
To validate our machine learning model we will calculate the weighed mutation score and cluster accuracy based on the clusters calculated by the model.
This is the same validation method as described in Chapter \ref{ch:exp1_validation}.
We will use the mutants of projects that are not selected for training as input for validating the model.
As described in Chapter \ref{ch:training_strategy} the projects should represent approximately 20\% of the total amount of mutants in our data set.
It may be possible the model has to cluster mutants it has never seen before.
We will use the same statistical significance threshold as in our firsts experiment to decide whether we will accept or reject or hypothesis.
To make our results reproducible we will select a random mutant based on a generated seed.
The seed generated for each run will be included in the results and can be found in the Github repository\cite{rbasarat-repo}.
\end{document}

>>>>

\subsection{Training strategy}
\label{ch:training_strategy}
Our data set contains of mutants represented by their characteristics. 
The characteristics of the mutants are generated per project and have a project specific context.
The relations between the different mutants are also specific per project.
For example mutant with a mutator in a certain project can have a different effect on the source code and can give other results than a mutator in a different project.
To keep the relations and context we decided to train a separate model per project.
\newline
To validate the model we need to split our data set into a training set and a validation set.
Our total data set consists of approximately 1 million mutants generated over fourteen projects.
Research has shown that if the data set is big enough a ratio of 80/20 is sufficient\cite{Guyon1997ARatio}.
We will divide each source projects into training and validation groups to reflect the 80/20 ratio as best as possible.
Depending on the amount of mutants per project we might not achieve a perfect 80/20 ratio.
The division of the mutants will be done randomly. 
To make our results reproducible we will select a random division based on a generated seed.
The seed generated for each run will be included in the results and can be found in the Github repository\cite{rbasarat-repo}.

@@

\subsection{Validation}
To validate our machine learning model we will calculate the weighed mutation score and cluster accuracy based on the clusters calculated by the model.
This is the same validation method as described in Chapter \ref{ch:exp1_validation}.
We will use the mutants of projects that are not selected for training as input for validating the model.
As described in Chapter \ref{ch:training_strategy} the projects should represent approximately 20\% of the total amount of mutants in our data set.
It may be possible the model has to cluster mutants it has never seen before.
We will use the same statistical significance threshold as in our firsts experiment to decide whether we will accept or reject or hypothesis.
To make our results reproducible we will select a random mutant based on a generated seed.
We will repeat our experiment 30 times with 30 different seeds.
Achieving consistent results while applying random selection and cluster initialization will contribute to the validity of the experiment.
The seed generated for each run will be included in the results and can be found in the Github repository\cite{rbasarat-repo}.

\end{document}
